Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Byzantium revision (\YellowPaperVersionNumber{})}}

### 2018-01-25 Paper.tex
move \hypertarget{Exceptional_Halting_function_Z}{exceptional halting} and 2 \hyperlink{Exceptional_Halting_function_Z}{exceptional halting}

We also assume the fixed amounts of $\mathbf{\delta}$ and $\mathbf{\alpha}$, specifying the stack items removed and added, both subscriptable on the instruction and an instruction cost function $C$ evaluating to the full cost, in gas, of executing the given instruction.

\subsubsection{Exceptional Halting}

@@

&&&& where $x=0$ if the code execution for this operation failed due to an exceptional halting\\

@@

&&&& where $x=0$ if the code execution for this operation failed due to an exceptional halting \\

>>>>

We also assume the fixed amounts of $\mathbf{\delta}$ and $\mathbf{\alpha}$, specifying the stack items removed and added, both subscriptable on the instruction and an instruction cost function $C$ evaluating to the full cost, in gas, of executing the given instruction.
\hypertarget{Exceptional_Halting_function_Z}{}
\subsubsection{Exceptional Halting}

@@

&&&& where $x=0$ if the code execution for this operation failed due to an \hyperlink{Exceptional_Halting_function_Z}{exceptional halting}\\

@@

&&&& where $x=0$ if the code execution for this operation failed due to an \hyperlink{Exceptional_Halting_function_Z}{exceptional halting} \\
